---
title: "Analize results"
output: html_notebook
---

```{r setup, warning=FALSE}
# CHANGE TO THE CORRESPONDING WORKING DIRECTORY
knitr::opts_knit$set(root.dir = '/home/harpo/Dropbox/ongoing-work/git-repos/goat-behavior/')
#knitr::opts_knit$set(root.dir = '/home/rodralez/hostdir/jobs/demand-planning/')
```

```{r}
library(dplyr)
suppressWarnings(suppressPackageStartupMessages(library(yardstick)))
```

```{r}
source("code/R/functions/train_model_loocv.R")
test_results <- readRDS("models/test_loocv/seba-caprino_model_test_loocv_results.rds")
byclass <- lapply(test_results,function(x) x$byclass)

     rownames <- do.call(rbind, byclass)   %>% rownames()
  byclass<-do.call(rbind, byclass) %>% as.data.frame() %>% 
    tibble::add_column(class =rownames) %>% 
    group_by(class) %>% 
    summarise(looSens_mean = mean(Sensitivity, na.rm =TRUE), 
              looSens_sd =sd(Sensitivity, na.rm=TRUE),
              looSpec_mean = mean(Specificity, na.rm =TRUE), 
              looSpec_sd=sd(Specificity, na.rm=TRUE),
              looBAcc_mean = mean(`Balanced Accuracy`, na.rm =TRUE), 
              looBAcc_sd=sd(`Balanced Accuracy`, na.rm=TRUE),
              looPrec_mean = mean(`Precision`, na.rm =TRUE), 
              looPrec_sd =sd(`Precision`, na.rm=TRUE),
    )
  
  
metrics<-loocv_peformance_metrics(test_results)


a<-c(metrics$overall,metrics$macro)
names(a) %>% gsub(pattern = "(loo)(*.)", replacement = "\\1Test\\2", x = names(a))
```
# Calculate Caret confusion metric

Most of the metrics does not consider MICRO and MACRO

```{r}
dataset <- readr::read_delim("data/split/seba-caprino_loocv.tsv",delim='\t')
goat_model <- readRDS("models/boost/seba-caprino_model.rds")

predictions<-predict(goat_model,dataset)
cm<-caret::confusionMatrix(reference=as.factor(dataset$Activity),predictions,mode="everything")
cm$overall

dataset %>% group_by(Anim,Activity) %>% count()
 samples<-create_loocv_samples(dataset) 
samples
```
```{r}
reshape2::melt(table(as.factor(predictions),as.factor(dataset$Activity))) %>% mutate(value=(value))  %>%   
  group_by(Var2) %>% mutate(total=sum(value),percent=value/total) %>% ungroup() %>%
  
  ggplot(aes(x=Var1,y=Var2))+
  geom_tile(aes(fill=percent), colour = "white") + 
   geom_text(aes(label = sprintf("%d", value,percent*100)), color='black',vjust = 1)+
   geom_text(aes(label = sprintf("(%1.1f%%)", percent*100)), color='black',vjust = 5,size=2.5)+
  scale_fill_gradient(low = "white", high = "orange")+
  xlab(" Predicted Activity ")+ylab(" Actual Activity")+
  theme_minimal()+ theme(legend.position = "none")


```

```{r}
source("code/R/functions/train_model.R")
results<-predict_activity(model = goat_model,dataset = dataset)

results$overall
results$macro

```


## Calculate MACRO performance metrics.
Kappa and Accuracy are the same as in caret confusion matrix. However, sens, spec and prec can differ when using MACRO or MICRO.

```{r}
macro_test_results<-data.frame(observations=as.factor(dataset$Activity),predictions=predictions)
rbind(
yardstick::accuracy(macro_test_results, 
         estimate=predictions,
         truth=observations,
         estimator="macro"),

yardstick::kap(macro_test_results,
         estimate=predictions,
         truth=observations,
         estimator="macro"),

yardstick::sensitivity(macro_test_results,
         estimate=predictions,
         truth=observations,
         estimator="macro"),


yardstick::specificity(macro_test_results,
         estimate=predictions,
         truth=observations,
         estimator="macro"),

yardstick::precision(macro_test_results,
         estimate=predictions,
         truth=observations,
         estimator="macro")
) %>% reshape2::melt() %>% select(.metric,value)
```


## calculate macro performance metrics per class

According the these results, the metrics provided by the `caret` package are correct since there is no difference between MACRO and MACRO.
Notice, however, the problem for calculating specificity per class using the `yardstick` package

```{r warning=FALSE}
macro_test_results<-data.frame(observations=as.factor(dataset$Activity),predictions=predictions)


yardstick::sensitivity(macro_test_results %>% filter(observations=="R"),
         estimate=predictions,
         truth=observations,
         estimator="macro") 

yardstick::precision(macro_test_results %>% filter(predictions=="R"),
         estimate=predictions,
         truth=observations,
         estimator="macro") 

```

```{r}
macro_test_results %>% precision(predictions,observations)
```

`


## Resample

The idea is to apply and 1 vs all approach. We convert each class to 1 and the rest to 0 and then we apply the performance metric.
```{r}
goat_model$pred %>% mutate(pred=ifelse(pred=="G",1,0),
                           obs=ifelse(obs=="G",1,0)) %>% mutate(pred=as.factor(pred),obs=as.factor(obs)) %>%
  group_by(Resample) %>% 
    yardstick::specificity(obs,pred) %>% summarise(reSens_G_Mean=mean(.estimate),reSens_G_sd=sd(.estimate)) 
   
```


```{r warning=FALSE}
  goat_model$pred %>% group_by(Resample,obs) %>% 
    yardstick::specificity(obs,pred) %>% group_by(obs) %>% 
    summarise(reSens_G_Mean=mean(.estimate),reSens_G_sd=sd(.estimate)) %>% 
    filter(obs == "G") %>% select(-obs)
```

## Metrics per animal
```{r}
confusion_matrix_plot<-function(pred,ref){
  

plot<-reshape2::melt(table(as.factor(pred),as.factor(ref))) %>% mutate(value=(value))  %>%   
  group_by(Var2) %>% mutate(total=sum(value),percent=value/total) %>% ungroup() %>%
   ggplot(aes(x=Var1,y=Var2))+
  geom_tile(aes(fill=percent), colour = "white") + 
   geom_text(aes(label = sprintf("%d", value,percent*100)), color='black',vjust = 1,size=15)+
   geom_text(aes(label = sprintf("(%1.1f%%)", percent*100)), color='black',vjust = 5,size=8)+
  scale_fill_gradient(low = "white", high = "orange")+
  xlab(" Predicted Activity ")+ylab(" Actual Activity")+
  theme_minimal()+ theme(legend.position = "none",
                         axis.title=element_text(size=30,face="bold"),
                         axis.text=element_text(size=25)
                         )

plot
}
```


```{r fig.height=12, fig.width=12}
results<-readRDS("models/test_loocv/seba-caprino_model_test_loocv_results.rds")
results[[8]]$byclass
  byclass <- lapply(results, function(x)
    x$byclass)
byclass
  rownames <- do.call(rbind, byclass)   %>% rownames()
  
   byclass<-do.call(rbind, byclass) %>% as.data.frame() 
  byclass<- byclass %>% select(Sensitivity,Specificity,Precision)
byclass %>% tibble::rownames_to_column() %>% readr::write_csv("/home/harpo/Dropbox/t.csv")


confusion_matrix_plot(results[[7]]$predictions, results[[7]]$observations)
confusion_matrix_plot(results[[8]]$predictions, results[[8]]$observations)
confusion_matrix_plot(results[[9]]$predictions, results[[9]]$observations)
```


# SHAP Values
```{r}
dataset <- readr::read_delim("data/split/seba-caprino_loocv.tsv",delim='\t')
goat_model <- readRDS("models/boost/seba-caprino_model.rds")
```





```{r}
library(doMC)
registerDoMC(cores = 10)

model <- goat_model
nsim<-20
```






## Calculate SHAP per animal and activity
```{r}
library(readr)
source("code/R/functions/calculate_shap.R")
source("code/R/functions/plot_shap.R")

dataset <-
  readr::read_delim("data/split/seba-caprino_loocv.tsv", delim = '\t')
goat_model <- readRDS("models/boost/seba-caprino_model.rds")
predictions <- predict(goat_model, dataset)
selected_variables <-
  readr::read_delim(
    "data/topnfeatures/seba-caprino_selected_features.tsv",
    col_types = cols(),
    delim = '\t'
  )
new_dataset <-
  dataset %>% select(selected_variables$variable, Anim, Activity)
new_dataset <- cbind(new_dataset, predictions)

shap_values <- calculate_shap(new_dataset, goat_model, nsim = 30)
shap_values

```



```{r}
library(doMC)
doMC::registerDoMC(cores =4)
```

## Overall plots
### Mean SHAP 
```{r fig.height=3, fig.width=6, message=FALSE, warning=FALSE}
source("code/R/functions/plot_shap.R")
pall<-shap_summary_plot(shap_values)
pall+xlim(0,0.35)
```


```{r fig.height=3, fig.width=6, message=FALSE, warning=FALSE}
pW<-shap_summary_plot_perclass(shap_values, class= "W",color="#C77CFF")+xlab("Activity W")+xlim(0,0.25)
pGM<-shap_summary_plot_perclass(shap_values, class= "GM",color="#7CAE00")+xlab("Activity GM")+xlim(0,0.25)
pG<-shap_summary_plot_perclass(shap_values, class= "G",color="#F8766D")+xlab("Activity G")+xlim(0,0.25)
pR<-shap_summary_plot_perclass(shap_values, class= "R",color="#00BFC4")+xlab("Activity R")+xlim(0,0.25)

grid.arrange(pW,pR,pG,pGM)
```


```{r fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
plotly::ggplotly(p)
```


```{r fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
shap_beeswarm_plot(shap_values,new_dataset)+labs(title="")
```


### Dependency plots

A new dependency plot considering activities and FP/TP

```{r fig.height=4, fig.width=8, include=FALSE}
source("code/R/functions/plot_shap.R")

li<-list()
li[[1]]<-dependency_plot("Steps",dataset = new_dataset,shap=shap_values)
li[[2]]<-dependency_plot("prev_steps1",dataset = new_dataset,shap=shap_values)
li[[3]]<-dependency_plot("%HeadDown",dataset = new_dataset,shap=shap_values)
li[[4]]<-dependency_plot("prev_headdown1",dataset = new_dataset,shap=shap_values)
li[[5]]<-dependency_plot("Active",dataset = new_dataset,shap=shap_values)
li[[6]]<-dependency_plot("prev_Active1",dataset = new_dataset,shap=shap_values)
li[[7]]<-dependency_plot("Standing",dataset = new_dataset,shap=shap_values)
li[[8]]<-dependency_plot("prev_Standing1",dataset = new_dataset,shap=shap_values)
li[[9]]<-dependency_plot("X_Act",dataset = new_dataset, shap=shap_values)
li[[10]]<-dependency_plot("Y_Act",dataset = new_dataset, shap=shap_values)
li[[11]]<-dependency_plot("DBA123",dataset = new_dataset, shap=shap_values)
li[[12]]<-dependency_plot("DFA123",dataset = new_dataset, shap=shap_values)
```

```{r fig.height=2, fig.width=10}
li[[2]]<-dependency_plot("prev_steps1",dataset = new_dataset,shap=shap_values)


plot<-grid.arrange(li[[3]])
#ggsave(plot = plot,"images/shap-values-depency_plot_headown.png",width = 10, height = 2.5, units = "in")
```

```{r fig.height=2, fig.width=10}
plot<-grid.arrange(li[[7]])
#ggsave(plot = plot,"images/shap-values-depency_plot_standing.png",width = 10, height = 2.5, units = "in")
```
```{r fig.height=2, fig.width=10}
plot<-grid.arrange(li[[5]])
#ggsave(plot = plot,"images/shap-values-depency_plot_active.png",width = 10, height = 2.5, units = "in")
```

```{r fig.height=4, fig.width=12}
plot<-grid.arrange(li[[11]][1,c(1,4)])
plot<-grid.arrange(li[[11]])
ggsave(plot = plot,"images/shap-values-depency_plot_dba123.png",width = 10, height = 2.5, units = "in")
```
```{r fig.height=4, fig.width=10}
plot<-grid.arrange(li[[12]][1,c(1,4)])
#ggsave(plot = plot,"images/shap-values-depency_plot_dfa123.png",width = 10, height = 2.5, units = "in")
```
```{r fig.height=14, fig.width=12}
do.call(grid.arrange, c(li, ncol = 1))
#ggsave(plot = plot,"images/shap-values-depency_plot_standing.png",width = 10, height = 2.5, units = "in")
```


### Analysis per animal

#### Dependecy Plots
##### Anim 13
```{r fig.height=10, fig.width=12, include=FALSE}
source("code/R/functions/plot_shap.R")
li<-list()
li[[1]]<-dependency_plot_anim("Steps",dataset = new_dataset,shap=shap_values,anim="a13")
li[[2]]<-dependency_plot_anim("prev_steps1",dataset = new_dataset,shap=shap_values,anim="a13")
li[[3]]<-dependency_plot_anim("%HeadDown",dataset = new_dataset,shap=shap_values,anim="a13")
li[[4]]<-dependency_plot_anim("prev_headdown1",dataset = new_dataset,shap=shap_values,anim="a13")
li[[5]]<-dependency_plot_anim("Active",dataset = new_dataset,shap=shap_values,anim="a13")
li[[6]]<-dependency_plot_anim("prev_Active1",dataset = new_dataset,shap=shap_values,anim="a13")
li[[7]]<-dependency_plot_anim("Standing",dataset = new_dataset,shap=shap_values,anim="a13")
li[[8]]<-dependency_plot_anim("prev_Standing1",dataset = new_dataset,shap=shap_values,anim="a13")
li[[9]]<-dependency_plot_anim("X_Act",dataset = new_dataset,shap=shap_values,anim="a13")
li[[10]]<-dependency_plot_anim("Y_Act",dataset = new_dataset,shap=shap_values,anim="a13")
#dev.off()
```


```{r fig.height=15, fig.width=8}
do.call(grid.arrange, c(li, ncol = 1))
```
##### Anim 5
```{r fig.height=2, fig.width=8, include=FALSE}
source("code/R/functions/plot_shap.R")
li<-list()
li[[1]]<-dependency_plot_anim("Steps",dataset = new_dataset,shap=shap_values,anim="a5")
li[[2]]<-dependency_plot_anim("prev_steps1",dataset = new_dataset,shap=shap_values,anim="a5")
li[[3]]<-dependency_plot_anim("%HeadDown",dataset = new_dataset,shap=shap_values,anim="a5")
li[[4]]<-dependency_plot_anim("prev_headdown1",dataset = new_dataset,shap=shap_values,anim="a5")
li[[5]]<-dependency_plot_anim("Active",dataset = new_dataset,shap=shap_values,anim="a5")
li[[6]]<-dependency_plot_anim("prev_Active1",dataset = new_dataset,shap=shap_values,anim="a5")
li[[7]]<-dependency_plot_anim("Standing",dataset = new_dataset,shap=shap_values,anim="a5")
li[[8]]<-dependency_plot_anim("prev_Standing1",dataset = new_dataset,shap=shap_values,anim="a5")
li[[9]]<-dependency_plot_anim("X_Act",dataset = new_dataset,shap=shap_values,anim="a5")
li[[10]]<-dependency_plot_anim("Y_Act",dataset = new_dataset,shap=shap_values,anim="a5")
#li[[8]]<-dependency_plot_anim("",dataset = new_dataset,shap=shap_values,anim="a5")
#dev.off()
```


```{r fig.height=20, fig.width=12}
do.call(grid.arrange, c(li, ncol = 1))
```
##### Anim 16
```{r include=FALSE}
source("code/R/functions/plot_shap.R")
li<-list()
li[[1]]<-dependency_plot_anim("Steps",dataset = new_dataset,shap=shap_values,anim="a16")
li[[2]]<-dependency_plot_anim("prev_steps1",dataset = new_dataset,shap=shap_values,anim="a16")
li[[3]]<-dependency_plot_anim("%HeadDown",dataset = new_dataset,shap=shap_values,anim="a5")
li[[4]]<-dependency_plot_anim("prev_headdown1",dataset = new_dataset,shap=shap_values,anim="a16")
li[[5]]<-dependency_plot_anim("Active",dataset = new_dataset,shap=shap_values,anim="a16")
li[[6]]<-dependency_plot_anim("prev_Active1",dataset = new_dataset,shap=shap_values,anim="a16")
li[[7]]<-dependency_plot_anim("Standing",dataset = new_dataset,shap=shap_values,anim="a16")
li[[8]]<-dependency_plot_anim("prev_Standing1",dataset = new_dataset,shap=shap_values,anim="a16")
```
 
```{r fig.height=14, fig.width=4}
do.call(grid.arrange, c(li, ncol = 1))
```
 
### Contribution Plots

##### Anim 13
```{r}
shap_values[which(shap_values$Anim == 'a13'),]
shap_values[which(shap_values$Anim == 'a13' &
                             shap_values$class == "GM"), 1:18]

```

###### class G
```{r fig.height=8, fig.width=12}

source("code/R/functions/calculate_shap.R")
source("code/R/functions/plot_shap.R")

anim_id <- 'a13'
activity <- 'G'
new_dataset_scaled <- new_dataset %>% mutate_if(is.numeric,range01)
new_dataset_scaled_filtered<-new_dataset_scaled[which(new_dataset_scaled$Anim == anim_id & new_dataset_scaled$Activity == activity),]

new_dataset_filtered<-new_dataset[ which(new_dataset$Anim == anim_id & new_dataset$Activity == activity),]
new_dataset_filtered

shap_values_G <- calculate_shap_class(new_dataset, new_data = new_dataset_filtered, goat_model, nsim = 100, p_function_G,"G")
shap_values_GM <- calculate_shap_class(new_dataset, new_data = new_dataset_filtered, goat_model, nsim = 100, p_function_GM,"GM")
p1 <- contribution_plot_w_feature(shap_values_G,new_dataset_scaled_filtered,num_row = 1) + labs(title="Anim a13: class G (FN)", subtitle = "SHAP analysis for class G") 
p2 <- contribution_plot_w_feature(shap_values_GM,new_dataset_scaled_filtered,num_row = 1) + labs(title="Anim a13: class G (FN)",subtitle = "SHAP analysis for class GM") 

p3 <- contribution_plot_w_feature(shap_values_G,new_dataset_scaled_filtered,num_row = 5) + labs(title="Anim a13: class G (TP)", subtitle = "SHAP analysis for class G") 
p4 <- contribution_plot_w_feature(shap_values_GM,new_dataset_scaled_filtered,num_row = 5) + labs(title="Anim a13: class G (TP)",subtitle = "SHAP analysis for class GM") 

grid.arrange(p3, p4, p1, p2, nrow = 2 )
list("G"=shap_values_G[5,1:15] %>% sum(),
"GM"=shap_values_GM[5,1:15] %>% sum()) %>% as.data.frame()
```

###### class GM
```{r fig.height=8, fig.width=12}
anim_id <- 'a13'
activity <- 'GM'
new_dataset_scaled <- new_dataset %>% mutate_if(is.numeric,range01)
new_dataset_scaled_filtered<-new_dataset_scaled[which(new_dataset_scaled$Anim == anim_id & new_dataset_scaled$Activity == activity),]

new_dataset_filtered<-new_dataset[ which(new_dataset$Anim == anim_id & new_dataset$Activity == activity),]
new_dataset_filtered


shap_values_G <- calculate_shap_class(new_dataset, new_data = new_dataset_filtered, goat_model, nsim = 100, p_function_G,"G")
shap_values_GM <- calculate_shap_class(new_dataset, new_data = new_dataset_filtered, goat_model, nsim = 100, p_function_GM,"GM")
p1 <- contribution_plot_w_feature(shap_values_GM,new_dataset_scaled_filtered,num_row = 8) + labs(title="Anim a13: class GM (FN)", subtitle = "SHAP analysis for class GM") 
p1
p2 <- contribution_plot_w_feature(shap_values_G,new_dataset_scaled_filtered,num_row = 8) + labs(title="Anim a13: class GM, (FN)",subtitle = "SHAP analysis for class G") 

p3 <- contribution_plot_w_feature(shap_values_GM,new_dataset_scaled_filtered,num_row = 2) + labs(title="Anim a13: class GM (TP)", subtitle = "SHAP analysis for class GM") 
p4 <- contribution_plot_w_feature(shap_values_G,new_dataset_scaled_filtered,num_row = 2) + labs(title="Anim a13: class GM (TP)",subtitle = "SHAP analysis for class G") 

grid.arrange(p3, 
             p4, 
             p1, 
             p2, nrow = 2 )

list("G"=shap_values_G[2,1:15] %>% sum(),
"GM"=shap_values_GM[2,1:15] %>% sum()) %>% as.data.frame()
```


#####  Anim 5
```{r}

shap_values[ which(shap_values$Anim == 'a5'),]
shap_values[which(shap_values$Anim == 'a5' &
                             shap_values$class == "GM"), 1:18]

```


###### class G
```{r fig.height=8, fig.width=12}
anim_id <- 'a5'
activity <- 'G'
new_dataset_scaled <- new_dataset %>% mutate_if(is.numeric,range01)
new_dataset_scaled_filtered<-new_dataset_scaled[which(new_dataset_scaled$Anim == anim_id & new_dataset_scaled$Activity == activity),]

new_dataset_filtered<-new_dataset[ which(new_dataset$Anim == anim_id & new_dataset$Activity == activity),]
new_dataset_filtered

shap_values_G <- calculate_shap_class(new_dataset, new_data = new_dataset_filtered, goat_model, nsim = 100, p_function_G,"G")
shap_values_GM <- calculate_shap_class(new_dataset, new_data = new_dataset_filtered, goat_model, nsim = 100, p_function_GM,"GM")
p1 <- contribution_plot_w_feature(shap_values_G,new_dataset_scaled_filtered,num_row = 3) + labs(title="Anim a5: Activity G (FN)", subtitle = "SHAP analysis for Activity G")  + ylim(c(-0.1,0.15))
p2 <- contribution_plot_w_feature(shap_values_GM,new_dataset_scaled_filtered,num_row = 3) + labs(title="Anim a5: Activity G (FN)",subtitle = "SHAP analysis for Activity GM")  + ylim(c(-0.1,0.15))

p3 <- contribution_plot_w_feature(shap_values_G,new_dataset_scaled_filtered,num_row = 1) + labs(title="Anim a5: Activity G (TP)", subtitle = "SHAP analysis for class G") + ylim(c(-0.1,0.15))
p4 <- contribution_plot_w_feature(shap_values_GM,new_dataset_scaled_filtered,num_row = 1) + labs(title="Anim a5: Activity G (TP)",subtitle = "SHAP analysis for Activity GM") + ylim(c(-0.1,0.15))


p3 + ylim(0,1)

grid.arrange(p3, p4, p1, p2, nrow = 2 )
list("G"=shap_values_G[1,1:15] %>% sum(),
"GM"=shap_values_GM[1,1:15] %>% sum()) %>% as.data.frame()
```
```{r}
plot <- grid.arrange(p1,p2,ncol =2)
#ggsave(plot = plot,"images/shap-values-contribution-plot-a5-G-FN.png",width = 8.5, height = 3.0, units = "in")
```

###### class GM
```{r fig.height=8, fig.width=12}
anim_id <- 'a5'
activity <- 'GM'
new_dataset_scaled <- new_dataset %>% mutate_if(is.numeric,range01)
new_dataset_scaled_filtered<-new_dataset_scaled[which(new_dataset_scaled$Anim == anim_id & new_dataset_scaled$Activity == activity),]

new_dataset_filtered<-new_dataset[ which(new_dataset$Anim == anim_id & new_dataset$Activity == activity),]
new_dataset_filtered


shap_values_G <- calculate_shap_class(new_dataset, new_data = new_dataset_filtered, goat_model, nsim = 100, p_function_G,"G")
shap_values_GM <- calculate_shap_class(new_dataset, new_data = new_dataset_filtered, goat_model, nsim = 100, p_function_GM,"GM")
p5 <- contribution_plot_w_feature(shap_values_GM,new_dataset_scaled_filtered,num_row = 4) + labs(title="Anim a5: Activity GM (FN)", subtitle = "SHAP contribution for Activity GM") + ylim(-0.1,0.15)
p6 <- contribution_plot_w_feature(shap_values_G,new_dataset_scaled_filtered,num_row = 4) + labs(title="Anim a5: Activity GM (FN)",subtitle = "SHAP contribution for Activity G") + ylim(-0.1,0.15)

p7 <- contribution_plot_w_feature(shap_values_GM,new_dataset_scaled_filtered,num_row = 3) + labs(title="Anim a5: Activity GM (TP)", subtitle = "SHAP contribution for class GM")  + ylim(c(-0.1,0.15))
p8 <- contribution_plot_w_feature(shap_values_G,new_dataset_scaled_filtered,num_row = 3) + labs(title="Anim a5: Activity GM (TP)",subtitle = "SHAP contribution for Activity G")  + ylim(c(-0.1,0.15))

grid.arrange(p7, p8, p5, p6, nrow = 2 )
list("G"=shap_values_G[4,1:15] %>% sum(),
"GM"=shap_values_GM[4,1:15] %>% sum()) %>% as.data.frame()


shap_values_GM[4,]
```

```{r}
plot <- grid.arrange(p1,p2,ncol =2)
#ggsave(plot = plot,"images/shap-values-contribution-plot-a5-GM-FN.png",width = 8.5, height = 3.0, units = "in")
```
```{r}
plot <- grid.arrange(p5,p1,ncol =2)
#ggsave(plot = plot,"images/shap-values-contribution-plot-a5-GM-G-FN.png",width = 8.5, height = 3.0, units = "in")
```

#####  Anim 16
###### class G
```{r fig.height=4, fig.width=8}
anim_id <- 'a16'
activity <- 'G'
new_dataset_filtered<-new_dataset[ which(new_dataset$Anim == anim_id & new_dataset$Activity == activity),]
new_dataset_filtered


shap_values_G <- calculate_shap_class(new_dataset, new_data = new_dataset_filtered, goat_model, nsim = 200, p_function_G,"G")
shap_values_GM <- calculate_shap_class(new_dataset, new_data = new_dataset_filtered, goat_model, nsim =200, p_function_GM,"GM")
p1 <- contribution_plot(shap_values_G,num_row = 1) + labs(title="Anim a16: class G (FN)", subtitle = "SHAP contribution for class G") 
p2 <- contribution_plot(shap_values_GM,num_row = 1) + labs(title="Anim a16: class G (FN)",subtitle = "SHAP contribution for class GM") 

p3 <- contribution_plot(shap_values_G,num_row = 6) + labs(title="Anim a16: class G (TP)", subtitle = "SHAP contribution for class G") 
p4 <- contribution_plot(shap_values_GM,num_row = 6) + labs(title="Anim a16: class G (TP)",subtitle = "SHAP contribution for class GM") 



grid.arrange(p3, p4, p1, p2, nrow = 2 )
list("G"=shap_values_G[6,1:15] %>% sum(),
"GM"=shap_values_GM[6,1:15] %>% sum()) %>% as.data.frame()

```


```{r fig.height=4, fig.width=8}
predictions_2 <- predict(goat_model, dataset, type = 'prob')
prob_dataset<-cbind(new_dataset,predictions_2)
prob_dataset[ which(prob_dataset$Anim == anim_id & prob_dataset$Activity == activity),][6,]


```

###### class GM
```{r fig.height=4, fig.width=4}
anim_id <- 'a16'
activity <- 'G'
new_dataset_filtered<-new_dataset[ which(new_dataset$Anim == anim_id & new_dataset$Activity == activity),]
new_dataset_filtered


shap_values_G <- calculate_shap_class(new_dataset, new_data = new_dataset_filtered, goat_model, nsim = 100, p_function_G,"G")
shap_values_GM <- calculate_shap_class(new_dataset, new_data = new_dataset_filtered, goat_model, nsim = 100, p_function_GM,"GM")
#p1 <- contribution_plot(shap_values_G,num_row = 1) + labs(title="Anim a5: class G (FN)", subtitle = "SHAP analysis for class G") 
#p2 <- contribution_plot(shap_values_GM,num_row = 1) + labs(title="Anim a5: class G (FN)",subtitle = "SHAP analysis for class GM") 

p3 <- contribution_plot(shap_values_G,num_row = 1) + labs(title="Anim a16: class GM (TP)", subtitle = "SHAP analysis for class G") 
p4 <- contribution_plot(shap_values_GM,num_row = 1) + labs(title="Anim a16: class GM (TP)",subtitle = "SHAP analysis for class GM") 
grid.arrange(p3, p4, nrow = 2 )

list("G"=shap_values_G[,1:15] %>% sum(),
"GM"=shap_values_GM[1,1:15] %>% sum()) %>% as.data.frame()
```
```

