---
title: "OKLAHOMA models (leave-one-out) Journal Version"
output: html_notebook
---
```{r}
#library(ggalluvial)
library(ggdark)
library(dplyr)
library(ggplot2)
library(readr)
library(glmnet)
library(Boruta)
library(rpart)
library(randomForest)
library(rpart.plot)
library(caret)
library(catboost)
library(lubridate)
```
# DATA PREPARATION
```{r}
set.seed(19091974) 
```

## Loading ABDEL+MIMOSA Dataset

```{r}
data_caprino_ok<-readr::read_delim("../../../rawdata/seba-caprino-feature-engineering-seba-abdel.tsv",col_types = cols(),delim='\t')
data_caprino_ok$Anim <- as.factor(data_caprino_ok$Anim)
data_caprino_ok$collar <- as.factor(data_caprino_ok$collar)
data_caprino_ok$Tag <- as.factor(data_caprino_ok$Tag)
data_caprino_ok <- data_caprino_ok %>% na.omit()
data_caprino_ok %>% names()
names(data_caprino_ok)[14]<-"distance(m)"
names(data_caprino_ok)[17]<-"%HeadDown"


```

####  (RL and RS) vs the rest of the classes
```{r}
  data_caprino_ok<-data_caprino_ok %>% 
  mutate(Activity=ifelse(Activity %in% c("RS","RL"),"R",Activity))
```

## Removing problematic registers
- Activity labeled as OTHER
- Animals with very few activities

```{r}
data_caprino_ok<- data_caprino_ok %>% filter(Activity!="OTHER")
data_caprino_ok<- data_caprino_ok %>% filter(Anim!="505067")
data_caprino_ok %>% group_by(Anim) %>% summarise(n=n()) %>% arrange(desc(n))
```

## Creating lags variables

```{r}
act_timeseries<-data_caprino_ok  %>% 
  mutate(epoch= paste(Date,`Date/Time`) %>% mdy_hms())

act_timeseries <-
    act_timeseries %>% mutate(day = cut(
    as.POSIXct(act_timeseries$epoch, origin = "1950-01-01", tz = "GMT"),
    breaks = "1 day"
    )
  )

data_caprino_ok<-act_timeseries %>% arrange(epoch) %>% group_by(Anim) %>% 
  mutate(
      prev_Active1=lag(Active, order_by=Anim,n=1, default=0),
      prev_Active2=lag(Active, order_by=Anim,n = 2, default=0 ),
      prev_Active3=lag(Active, order_by=Anim,n = 3, default=0 )
      ) %>% 
   mutate(
      prev_Standing1=lag(Standing, order_by=Anim,n=1, default=0),
      prev_Standing2=lag(Standing, order_by=Anim,n = 2, default=0 ),
      prev_Standing3=lag(Standing, order_by=Anim,n = 3, default=0 )
      ) %>%
   mutate(
      prev_Lying1=lag(Lying, order_by=Anim,n=1, default=0),
      prev_Lying2=lag(Lying, order_by=Anim,n = 2, default=0 ),
      prev_Lying3=lag(Lying, order_by=Anim,n = 3, default=0 )
      ) %>%
     mutate(
      prev_steps1=lag(Steps, order_by=Anim,n=1, default=0),
      prev_steps2=lag(Steps, order_by=Anim,n = 2, default=0 ),
      prev_steps3=lag(Steps, order_by=Anim,n = 3, default=0 )
      ) %>%
    mutate(
      prev_headdown1 = lag(
        `%HeadDown`,
        order_by = Anim,
        n = 1,
        default = 0
      ),
      prev_headdown2 = lag(
        `%HeadDown`,
        order_by = Anim,
        n = 2,
        default = 0
      ),
      prev_headdown3 = lag(
        `%HeadDown`,
        order_by = Anim,
        n = 3,
        default = 0
      )
    )

act_timeseries %>% filter(Anim=="1553") %>% mutate(prev_headdown1 = lag(
        `%HeadDown`,
       
        n = 1,
        default = 0
      ))
```


## Removing useless variables according to expertise

```{r}
data_caprino_ok <- data_caprino_ok %>% ungroup() %>% select(-lat,
                                                                            -long,
                                                                           # -Anim,
                                                                            -Diffxy,
                                                                            -Meanxy,
                                                                            -Varxy,
                                                                            -logdistance,
                                                                            -SMA
                                                                            #,-DOP
                                                            )
```

## Selecting only numeric features
```{r}
data_caprino_ok_numeric<-data_caprino_ok %>% select(-'Date/Time',-Date,-epoch) %>% select_if(~class(.) == 'numeric')
data_caprino_ok_numeric<-data_caprino_ok_numeric %>% tibble::add_column(Anim=data_caprino_ok$Anim)

data_caprino_ok_numeric <- data_caprino_ok_numeric #%>% select(
#  -"distance(m)",
#  -Steps,
#  -X_Act,
#  -Y_Act,
#  -DFL1,
#  -DFL2,
#  -DFL3,
#  -DFA12,
#  -DFA123,
#  -DBL1,
#  -DBL2,
#  -DBL3,
#  -DBA12,
#  -DBA123,
#   -DOP
 # -tag_activity,
#)
names(data_caprino_ok_numeric) %>% as.data.frame()
```


# FEATURE ENGINEERING


## Creating new variables according to several papers
```{r}
data_caprino_ok_numeric <-
  data_caprino_ok_numeric %>% mutate(DiffXY = abs(X_Act - Y_Act))
data_caprino_ok_numeric <-
  data_caprino_ok_numeric %>% rowwise() %>% mutate(MeanXY = mean(c(X_Act, Y_Act)))
data_caprino_ok_numeric <-
  data_caprino_ok_numeric %>% rowwise() %>% mutate(VarXY = sd(c(X_Act, Y_Act)))

# Scale distance and steps
range01 <- function(x){(x-min(x))/(max(x)-min(x))}
data_caprino_ok_numeric %>% mutate(Steps=range01(Steps),`distance(m)`=range01(`distance(m)`))

data_caprino_ok_numeric <- data_caprino_ok_numeric %>%  mutate(
  X_Actlog = log10(X_Act + 1e-10),
  Y_Actlog = log10(Y_Act + 1e-10),
  Stepslog = log10(Steps + 1e-10),
 `distance(m)log` = log10(`distance(m)` + 1e-10),
  VarXYlog = log10(VarXY + 1e-10),
  DiffXYlog = log10(DiffXY + 1e-10),
  MeanXYlog = log10(MeanXY + 1e-10),
  DOPlog = log10(DOP + 1e-10)
)

#data_caprino_ok_numeric$tag_activity<-data_caprino_ok_numeric %>% select(Active,Lying,Standing) %>% apply( MARGIN=1, FUN=which.max)# %>% as.factor()
data_caprino_ok_numeric<-data_caprino_ok_numeric %>% ungroup()

names(data_caprino_ok_numeric) %>% as.data.frame()

data_caprino_ok_numeric <- data_caprino_ok_numeric %>% select(#-`distance(m)`,
                                                              -`distance(m)log`,
                                                              #-Stepslog,
                                                              -Steps,
                                                              -X_Act,
                                                              -Y_Act,
                                                              #-Active,
                                                              #-Lying,
                                                              #-Standing,
                                                            
                                                              -VarXY,
                                                              -DiffXY,
                                                              -MeanXY,
                                                              #-tag_activity,
                                                            
                                                              -DOP,
                                                              -DOPlog
                                                              )

names(data_caprino_ok_numeric) %>% as.data.frame()
```
## BORUTA selecting Animals 

We use ~40% of the dataset for selecting features using BORUTA algorithm. 
Four animals were removed.

```{r}
data_caprino_ok_numeric %>% group_by(Anim) %>% summarise(n=n())
train_dataset_boruta<- data_caprino_ok_numeric  %>% 
  tibble::add_column(Activity=as.factor(data_caprino_ok$Activity))

data_caprino_ok_numeric_w_classes<- train_dataset_boruta %>% filter(!(Anim %in% c(1553,1635,1779,505081,505075,505080) ))
train_dataset_boruta<- train_dataset_boruta %>% filter((Anim %in% c(1553,1635,1779,505081,505075,505080) ))  %>% select(-Anim)
train_dataset_boruta %>% group_by(Activity) %>% summarise(n=n())
data_caprino_ok_numeric_w_classes %>% group_by(Activity) %>% summarise(n=n())

#data_caprino_ok_numeric$Anim %>% unique()
```

## Bootstraping

```{r}
resamples<-rsample::bootstraps(train_dataset_boruta,strata = Activity,times = 30  )
```


## Using BORUTA for Feature Selection


### Select TOP N features
```{r}
source("../functions/select_features_boruta.R")
library(doMC)
registerDoMC(cores = 4)
library(rsample)
var_importance <- foreach(i = 1:length(resamples$splits), .combine = rbind) %dopar% {
  trainset<- rsample::analysis(resamples$splits[[i]])
  partial<-select_features_boruta(trainset, "Activity",20)
  partial<-cbind(partial,rsample=i)
}  

var_always_present<-var_importance %>% group_by(variable) %>% summarise(n=n()) %>% filter(n==30) %>% ungroup() %>% select(variable)
v<-var_always_present %>% unlist() %>% unname()



var_importance_boruta_final<- var_importance %>% filter(variable %in% v) %>% group_by(variable) %>% summarise(grandmeanImp=mean(meanImp)) %>% arrange(grandmeanImp %>% desc()) %>% ungroup() %>% select(variable)

var_importance_boruta_final <-
    apply(var_importance_boruta_final$variable %>% t() , 2,
          function(x)
            stringr::str_replace_all(x,
                                     pattern = "`",
                                     replacement = "")) %>% as.data.frame()
names(var_importance_boruta_final) <- "variable"
var_importance_boruta_final %>% arrange(variable)
```


# MODELS
## Macro and Micro metrics

```{r}

metrics <- function(cm,preds,testset) {
  macro_metrics <- (apply(cm$byClass, 2, sum) / 4) [c(5, 6, 7)]
  s = table(preds, as.factor(testset$Activity))
  Precision_micro <-  (sum(diag(s)) / sum(apply(s, 1, sum)))
  Recall_micro <- (sum(diag(s)) / sum(apply(s, 2, sum)))
  micro_metrics <- c((sum(diag(s)) / sum(apply(s, 1, sum))),
                     (sum(diag(s)) / sum(apply(s, 2, sum))),
                     2 * ((Precision_micro * Recall_micro) / (Precision_micro + Recall_micro)
                     ))
  mm <- cbind(c(macro_metrics), c(micro_metrics))
  data.frame(macro = mm[, 1], micro = mm[, 2])
}
```

## Create LOOCV samples
```{r}

#data_caprino_ok_numeric <- data_caprino_ok_numeric %>%  filter( !(Anim %in% c(1553,1635,505081,505075) ))
loocv_sample_train <- vector(mode = "list", length = length( data_caprino_ok_numeric_w_classes$Anim %>% unique()))
loocv_sample_test <- vector(mode = "list", length = length( data_caprino_ok_numeric_w_classes$Anim %>% unique()))

n_anim<-data_caprino_ok_numeric_w_classes$Anim %>% unique()

for(i in seq_along(n_anim) ) {
  print(i)
  loocv_sample_train[[i]] <- which(data_caprino_ok_numeric_w_classes$Anim != n_anim[i])
  loocv_sample_test[[i]] <- which(data_caprino_ok_numeric_w_classes$Anim == n_anim[i])
}

loocv_sample_test[[1]]
n_anim
```

## Control and Resampling setup
```{r}
ctrl_fast <- trainControl(
  method = "cv",
  number = 10,
  returnResamp = 'final',
  savePredictions = 'final',
  verboseIter = FALSE,
  classProbs = TRUE,
  allowParallel = TRUE,
  summaryFunction=multiClassSummary
)
```

## Grid Search parameters

```{r}
 grid <- expand.grid(
    depth = c(4),
    learning_rate = c(0.05),
    #iterations = c(10,50,100,500,1000),
    iterations = c(1000),
    l2_leaf_reg = c(3.0),
    #regularization parameter
    rsm = c(1),
    # percentage of features to use at each split selection
    border_count = c(64)
  )
```

## Boost Boruta Dataset

```{r}

  boost_val_dataset_feature_selection <- train_dataset_boruta %>% sample_frac(.2)
  trainset_dataset_feature_selection <- setdiff(train_dataset_boruta, boost_val_dataset_feature_selection)
  
  selected_variables <- var_importance_boruta_final 
  boostFit_boruta <- caret::train(
    x = trainset_dataset_feature_selection %>%
      select(selected_variables$variable) %>%  na.omit() %>% as.data.frame(),
    y = trainset_dataset_feature_selection %>%  select(Activity) %>% unlist() %>% unname()  %>% as.factor(),
    method = catboost::catboost.caret,
    tuneGrid = grid,
    metric = 'logLoss',
    verbose = 0,
    trControl = ctrl_fast,
    auto_class_weights = "Balanced",
    use_best_model = TRUE,
    od_type = 'Iter',
    test_pool = catboost.load_pool(
      boost_val_dataset_feature_selection %>%
        select(selected_variables$variable) %>%  na.omit() %>% as.data.frame(),
      label = as.numeric(as.factor(boost_val_dataset_feature_selection$Activity)) -
        1
    )
  )
boostFit_boruta
```


## Boost LOOCV

```{r message=FALSE}
library(caret)
library(doMC)
registerDoMC(cores = 8)
#caret_dataset <-  cbind(data_caprino_ok_numeric,Activity=data_caprino_ok$Activity)
caret_dataset <-  data_caprino_ok_numeric_w_classes
caret_dataset <- readr::read_delim("../../../data/split/seba-caprino_loocv.tsv",delim='\t')
loocv_results<- vector(mode = "list", length = length( n_anim))

for (i in seq(1, length(n_anim))) {
  train_dataset_loocv <- caret_dataset[loocv_sample_train[[i]], ]
  train_dataset_loocv$Activity <-
    as.factor(train_dataset_loocv$Activity)
  test_dataset_loocv <- caret_dataset[-loocv_sample_train[[i]], ]
  test_dataset_loocv$Activity <-
    factor(test_dataset_loocv$Activity,
           levels = levels(train_dataset_loocv$Activity))
  #print(train_dataset[-loocv_sample[[i]],] %>% group_by(Activity) %>% summarise(n=n()))
  
  
  boost_val_dataset <- train_dataset_loocv %>% sample_frac(.1)
  trainset_dataset <- setdiff(train_dataset_loocv, boost_val_dataset)
  
  selected_variables <- var_importance_boruta_final #%>% filter(variable!="MeanXYlog") %>% 
  #filter(variable!="DFA123") %>%
  #filter(variable!="DBA123") %>%
  #filter(variable!="DFA12") %>%
  #filter(variable!="DBL2") %>%
  #filter(variable!="X_Actlog")
  
 
  
  boostFit <- caret::train(
    x = trainset_dataset %>%
      select(selected_variables$variable) %>%  na.omit() %>% as.data.frame(),
    y = trainset_dataset %>%  select(Activity) %>% unlist() %>% unname()  %>% as.factor(),
    method = catboost::catboost.caret,
    #tuneLength=5,
    tuneGrid = grid,
    metric = 'logLoss',
    #preProcess = c("center","scale"),
    verbose = 0,
    trControl = ctrl_fast,
    auto_class_weights = "Balanced",
    #class_weights= py$class_weight,
    use_best_model = TRUE,
    od_type = 'Iter',
    test_pool = catboost.load_pool(
      boost_val_dataset %>%
        select(selected_variables$variable) %>%  na.omit() %>% as.data.frame(),
      label = as.numeric(as.factor(boost_val_dataset$Activity)) -
        1
    )
  )
  boostFit
  boostFit$finalModel
  
  ## Independent Evaluation
  boostFit_eval <- predict(boostFit,
                           test_dataset_loocv  %>%
                             select(selected_variables$variable))
  cm <-
    confusionMatrix(reference = as.factor(test_dataset_loocv$Activity), boostFit_eval)
  #metrics(cm, boostFit_eval, test_dataset_loocv)
  
  loocv_results[[i]] <- list(
        overall = cm$overall,
        byclass = cm$byClass,
        tab = cm$table,
        predictions = boostFit_eval,
        model = boostFit
      )
}
#loocv_results
```


# RESULTS
```{r}
overall<-lapply(loocv_results,function(x) x$overall %>% t() %>% 
                  as.data.frame() %>% 
                  select(Accuracy)) %>% unlist() %>% t() 
overall  %>% mean()
overall  %>% sd()

byclass <- lapply(loocv_results, function(x)
  x$byclass)

rownames <- do.call(rbind, byclass)   %>% rownames()

do.call(rbind, byclass) %>% as.data.frame() %>% 
  tibble::add_column(class =rownames) %>% 
  group_by(class) %>% 
  summarise(mean = mean(Recall, na.rm =TRUE), sd=sd(Recall, na.rm=TRUE)
            )
```
