---
title: "Tables and others for article"
output: html_notebook
---
```{r setup}
library(dplyr)
library(tidyr)
library(yaml)
library(dplyr)
library(ggplot2)
```

# Functions
## Function for resample table
```{r}

create_resampling_restable <- function (experiment_id, experiments_data){
library(ztable)
library(tibble)
activity_metrics <-
  experiments_data %>% filter(Experiment == experiment_id) %>% select(
    Experiment,
    reSens_R_Mean,
    reSens_GM_Mean,
    reSens_W_Mean,
    reSens_G_Mean,
    rePrec_R_Mean,
    rePrec_GM_Mean,
    rePrec_W_Mean,
    rePrec_G_Mean,
    reSpec_R_Mean,
    reSpec_GM_Mean,
    reSpec_W_Mean,
    reSpec_G_Mean
  ) %>%
  tidyr::pivot_longer(
    !Experiment,
    names_to = c("Activity", "Metric"),
    names_pattern = "re(.*)_(.*)_Mean",
    values_to = "count"
  ) %>%
  tidyr::pivot_wider(names_from = Metric, values_from = c(count)) %>% as.data.frame() %>% select(!Experiment)

all_metrics <-
  experiments_data %>% filter(.data$Experiment == experiment_id) %>% select(
    Experiment,
    reAcc_Mean,
    reKappa_Mean,
    reSens_Mean,
    reSens_Mean,
    rePrec_Mean,
    reSpec_Mean
  ) %>% t() %>% as.data.frame()

all_metrics <- all_metrics %>% slice(2:6)
all_metrics$V1 <- as.double(all_metrics$V1)
all_metrics <- all_metrics %>%
  add_column(all_metrics) %>%
  add_column(all_metrics) %>%
  add_column(all_metrics) %>% rownames_to_column("Metrics")

all_metrics$Metrics <- c("Accuracy",
                         "Kappa",
                         "Sensitivity",
                         "Specificity",
                         "Precision")

activity_metrics <- activity_metrics %>% rename(Metrics = "Activity")
activity_metrics$Metrics <- c("Sensitivity", "Precision", "Specificity")

names(all_metrics) <- names(activity_metrics)
rgroup = c("Overall", "Per Activity")
n.rgroup = c(5, 3)

table_results <- 
rbind(all_metrics, activity_metrics) %>%
  ztable(align = "llllll") %>% spanCol(row = 2, from = 3, to =
                                                         6) %>%
  spanCol(row = 3, from = 3, to = 6) %>%
  spanCol(row = 4, from = 3, to = 6) %>%
  spanCol(row = 5, from = 3, to = 6) %>%
  spanCol(row = 5, from = 3, to = 6) %>%
  spanCol(row = 6, from = 3, to = 6) %>%
  addrgroup(rgroup = rgroup,
            n.rgroup = n.rgroup,
            cspan.rgroup = 1) %>% hlines(add = c(5))

table_results
}
```
## Function for loocv table
```{r}
create_loocv_restable <- function (experiment_id, experiments_data){
library(ztable)
library(tibble)
activity_metrics <-
  experiments_data %>% filter(Experiment == experiment_id) %>% select(
    Experiment,
    R_Sens,
    GM_Sens,
    W_Sens,
    G_Sens,
    R_Prec,
    GM_Prec,
    W_Prec,
    G_Prec,
    R_Spec,
    GM_Spec,
    W_Spec,
    G_Spec
  ) %>%
  tidyr::pivot_longer(
    !Experiment,
    names_to = c("Activity", "Metrics"),
    names_pattern = "^(.*)_(.*)$",
    values_to = "count"
  ) %>%
  tidyr::pivot_wider(names_from = Activity, values_from = c(count)) %>% as.data.frame() %>% select(!Experiment)

all_metrics <-
  experiments_data %>% filter(.data$Experiment == experiment_id) %>% select(
    Experiment,
    looAcc_mean_macro,
    looKappa_mean_macro,
    looSens_mean_macro,
    looPrec_mean_macro,
    looSpec_mean_macro,
  ) %>% t() %>% as.data.frame()

all_metrics <- all_metrics %>% slice(2:6)
all_metrics$V1 <- as.double(all_metrics$V1)
all_metrics <- all_metrics %>%
  add_column(all_metrics) %>%
  add_column(all_metrics) %>%
  add_column(all_metrics) %>% rownames_to_column("Metrics")

all_metrics$Metrics <- c("Accuracy",
                         "Kappa",
                         "Sensitivity",
                         "Specificity",
                         "Precision")

#activity_metrics <- activity_metrics %>% rename(Metrics = "Activity")
activity_metrics$Metrics <- c("Sensitivity", "Precision", "Specificity")

names(all_metrics) <- names(activity_metrics)
rgroup = c("Overall", "Per Activity")
n.rgroup = c(5, 3)

table_results <- 
rbind(all_metrics, activity_metrics) %>%
  ztable(align = "llllll") %>% spanCol(row = 2, from = 3, to =
                                                         6) %>%
  spanCol(row = 3, from = 3, to = 6) %>%
  spanCol(row = 4, from = 3, to = 6) %>%
  spanCol(row = 5, from = 3, to = 6) %>%
  spanCol(row = 5, from = 3, to = 6) %>%
  spanCol(row = 6, from = 3, to = 6) %>%
  addrgroup(rgroup = rgroup,
            n.rgroup = n.rgroup,
            cspan.rgroup = 1) %>% hlines(add = c(5))

table_results
}
```


```{r}
dataset %>% group_by(Anim) %>% count() %>% select(Anim)
dataset$Anim <- as.character(dataset$Anim)
dataset %>% mutate(Anim = replace(Anim, stringr::str_detect(Anim,"1553"), "a1"))
dataset %>% mutate(Anim = replace(Anim, stringr::str_detect(Anim,"1635"), "a2"))
dataset %>% mutate(Anim = replace(Anim, stringr::str_detect(Anim,"1636"), "a3"))
dataset %>% mutate(Anim = replace(Anim, stringr::str_detect(Anim,"1646"), "a4"))
dataset %>% mutate(Anim = replace(Anim, stringr::str_detect(Anim,"1677"), "a5"))
dataset %>% mutate(Anim = replace(Anim, stringr::str_detect(Anim,"1713"), "a6"))
dataset %>% mutate(Anim = replace(Anim, stringr::str_detect(Anim,"1779"), "a7"))
dataset %>% mutate(Anim = replace(Anim, stringr::str_detect(Anim,"505001"), "a8"))
dataset %>% mutate(Anim = replace(Anim, stringr::str_detect(Anim,"505019"), "a9"))
dataset %>% mutate(Anim = replace(Anim, stringr::str_detect(Anim,"505035"), "a10"))
dataset %>% mutate(Anim = replace(Anim, stringr::str_detect(Anim,"505048"), "a11"))
dataset %>% mutate(Anim = replace(Anim, stringr::str_detect(Anim,"505058"), "a12"))
dataset %>% mutate(Anim = replace(Anim, stringr::str_detect(Anim,"505071"), "a13"))
dataset %>% mutate(Anim = replace(Anim, stringr::str_detect(Anim,"505075"), "a14"))
dataset %>% mutate(Anim = replace(Anim, stringr::str_detect(Anim,"505080"), "a15"))
dataset %>% mutate(Anim = replace(Anim, stringr::str_detect(Anim,"505081"), "a16"))


dataset %>% group_by(Anim) %>% count() %>% select(Anim)
dataset %>% count()
```

```{r}
separate_anim <- c(
  "a1",
  "a2",
  "a3",
  "a7",
  "a10",
  "a14",
  "a15")

dataset %>% filter(Anim %in% separate_anim) %>% nrow()
```

# Generate dataset table
```{r}
library(kableExtra)
library(ztable)
options(ztable.type = "latex")
dataset <-
  readr::read_delim("../../../data/preprocessed/seba-caprino-preprocessed.tsv",
                    delim = "\t")
dataset_wide <-
  dataset %>%  group_by(Anim, Activity) %>% summarise (n = n()) %>% 
  ungroup() %>% pivot_wider(names_from = Anim,values_from = n,
                            values_fill = 0) %>%
  bind_rows(summarise(.,
                      across(where(is.numeric), sum),
                      across(where(is.character), ~ "Total"))) %>%  ungroup %>%
  
  
  select(Activity, 
        "a1",
        "a2",
        "a3",
        "a4",
        "a5",
        "a6",
        "a7",
        "a8",
        "a9",
        "a10",
        "a11",
        "a12",
        "a13",
        "a14",
        "a15",
        "a16")
dataset_wide <- dataset_wide %>% rowwise %>%
  mutate(Total = sum(across(2:17)))  %>% ungroup %>%
  as.data.frame() 
ztbl<-ztable(dataset_wide)#

ztbl %>% makeHeatmap(cols = 18) %>% print(caption="Table 1: Number of observations per animal discriminated by activity.")
```

# Generate DATASET A table
```{r results='asis'}

library(kableExtra)
library(ztable)
options(ztable.type = "latex")
dataset <-
  readr::read_delim("../../../data/split/seba-caprino_features.tsv",
                    delim = "\t")
dataset_wide <-
  dataset %>%  group_by(Anim, Activity) %>% summarise (n = n()) %>% 
  ungroup() %>% pivot_wider(names_from = Anim,values_from = n,
                            values_fill = 0) %>%
  bind_rows(summarise(.,
                      across(where(is.numeric), sum),
                      across(where(is.character), ~ "Total"))) %>%  ungroup %>%
  
    select(Activity, 
        "a1",
        "a2",
        "a3",
        "a8",
        "a4",
        "a10",
        "a15")

dataset_wide <- dataset_wide %>% rowwise %>%
  mutate(Total = sum(across(2:8)))  %>% ungroup %>%
  as.data.frame() 
ztable(dataset_wide) %>% makeHeatmap(cols = 9) %>%  print(caption="Table 2: Number of observations per animal discriminated by activity for Dataset A.")

```

# Generate DATASET B table
```{r}

library(kableExtra)
library(ztable)
options(ztable.type = "latex")
dataset <-
  readr::read_delim("../../../data/split/seba-caprino_loocv.tsv",
                    delim = "\t")
dataset_wide <-
  dataset %>%  group_by(Anim, Activity) %>% summarise (n = n()) %>% 
  ungroup() %>% pivot_wider(names_from = Anim,values_from = n,
                            values_fill = 0) %>%
  bind_rows(summarise(.,
                      across(where(is.numeric), sum),
                      across(where(is.character), ~ "Total"))) %>%  ungroup %>%
  
    select(Activity, 
      "a5",				
      "a6",				
      "a7",				
      "a9",
      "a11",				
      "a12",				
      "a13",				
      "a14",				
      "a16"
     )

dataset_wide <- dataset_wide %>% rowwise %>%
  mutate(Total = sum(across(2:10)))  %>% ungroup %>%
  as.data.frame() 

ztable(dataset_wide) %>% makeHeatmap(cols = 11) %>% print(caption="Table 3: Number of observations per animal discriminated by activity for Dataset B.")
dataset %>% group_by(Anim) %>% count()
```


# Features
```{r}
library(dplyr)
library(ztable)
options(ztable.type = "latex")
features_set<-googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1nivRPl44Kq6G5YP17xitUGOnksuZ66pjLKHqfM0gRJQ/edit?usp=sharing") 
rgroup=c("IceTag Monitor","GPS Collar","Derived from sensor input")
n.rgroup=c(4,4,15)


z<-features_set %>% select(-Type) %>% ztable(booktabs = T) %>%
    addrgroup(rgroup=rgroup,n.rgroup=n.rgroup,cspan.rgroup=3)
print(z)
```

# Calculate Resampling results per experiment 
use `dvc exp show --drop ".*" --keep "re.*|Experiment" --csv >resample_results.csv`
```{r}

options(ztable.type = 'viewer')
experiments <- c("5f-1s", "10f-1s", "15f-1s", "20f-1s", "25f-1s")
experiments_no_log <-
  c("5f-1s-no-log-1d-loocvtune",
    "10f-1s-no-log-1d-loocvtune",
    "15f-1s-no-log-1d-loocvtune",
    "20f-1s-no-log-1d-loocvtune",
    "25f-1s-no-log-1d-loocvtune",
    "30f-1s-no-log-1d-loocvtune",
    "35f-1s-no-log-1d-loocvtune"
    )
experiments <- c(experiments_no_log)
r2 <- readr::read_csv("../../../resample_results.csv")
r2 <- r2 %>% filter(Experiment %in% experiments)

#options(ztable.type = 'latex')
options(ztable.zebra=NULL)
create_resampling_restable("5f-1s-no-log-1d-loocvtune",r2)  
create_resampling_restable("10f-1s-no-log-1d-loocvtune",r2)
create_resampling_restable("15f-1s-no-log-1d-loocvtune",r2)
create_resampling_restable("20f-1s-no-log-1d-loocvtune",r2)
create_resampling_restable("25f-1s-no-log-1d-loocvtune",r2)
create_resampling_restable("30f-1s-no-log-1d-loocvtune",r2)
create_resampling_restable("35f-1s-no-log-1d-loocvtune",r2)
```
```{r}
create_resampling_restable("new-metrics-implementation",r2)  
```

## Plots
```{r fig.height=5, fig.width=10}

experiments_no_log <-
  c("5f-1s-no-log-1d-loocvtune",
    "10f-1s-no-log-1d-loocvtune",
    "15f-1s-no-log-1d-loocvtune",
    "20f-1s-no-log-1d-loocvtune",
    "25f-1s-no-log-1d-loocvtune",
    "30f-1s-no-log-1d-loocvtune",
    "35f-1s-no-log-1d-loocvtune"
    )
experiments <- c(experiments_no_log)
r2 <- readr::read_csv("../../../resample.csv")
r2 <- r2 |> filter(Experiment %in% experiments)
r2$id<-c(35,30,25,20,15,10,5) 
r2 <- r2 %>% arrange(id)
r2
```

```{r fig.height=6, fig.width=8}
sens<- r2 |> ggplot(aes(x=id))+
  ylab("Sensitivity")+
  xlab("Feature number")+
    ylim(c(0.5,1))+
  geom_point(aes(y=reSens_Mean))+
  geom_point(aes(x=15,y=max(reSens_Mean)),size=3,color='red')+
  geom_line(aes(y=reSens_Mean))+
  geom_ribbon(aes(ymax=reSens_Mean+reSens_sd, ymin=reSens_Mean-reSens_sd),alpha=0.1,fill="orange")+
  geom_line(aes(y=reSens_Mean+reSens_sd),color='orange')+
  geom_line(aes(y=reSens_Mean-reSens_sd),color='orange')+
  scale_x_continuous(breaks = seq(0,35,by = 5))+
  theme_linedraw()


bacc<- r2 |> ggplot(aes(x=id))+
  ylab(" Accuracy")+
  xlab("Feature number")+
  ylim(c(0.5,1))+
  geom_point(aes(y=reAcc_Mean))+
  geom_point(aes(x=15,y=max(reAcc_Mean)),size=3,color='red')+
  geom_line(aes(y=reAcc_Mean))+
  geom_ribbon(aes(ymax=reAcc_Mean+reAcc_sd, ymin=reAcc_Mean-reAcc_sd),alpha=0.1,fill="orange")+
  geom_line(aes(y=reAcc_Mean+reAcc_sd),color='orange')+
  geom_line(aes(y=reAcc_Mean-reAcc_sd),color='orange')+
  scale_x_continuous(breaks = seq(0,35,by = 5))+
  theme_linedraw()
  

spec<- r2 |> ggplot(aes(x=id))+
  ylab("Specificity")+
  xlab("Feature number")+
  ylim(c(0.5,1))+
  geom_point(aes(y=reSpec_Mean))+
  geom_point(aes(x=15,y=max(reSpec_Mean)),size=3,color='red')+
  geom_line(aes(y=reSpec_Mean))+
  geom_ribbon(aes(ymax=reSpec_Mean+reSpec_sd, ymin=reSpec_Mean-reSpec_sd),alpha=0.1,fill="orange")+
  geom_line(aes(y=reSpec_Mean+reSpec_sd),color='orange')+
  geom_line(aes(y=reSpec_Mean-reSpec_sd),color='orange')+
  scale_x_continuous(breaks = seq(0,35,by = 5))+
  theme_linedraw()
 

prec <- r2 |> ggplot(aes(x=id))+
  ylab("Precision")+
  xlab("Feature number")+
  ylim(c(0.5,1))+
  geom_point(aes(y=rePrec_Mean))+
  geom_point(aes(x=15,y=max(rePrec_Mean)),size=3,color='red')+
  geom_line(aes(y=rePrec_Mean))+
  geom_ribbon(aes(ymax=rePrec_Mean+rePrec_sd, ymin=rePrec_Mean-rePrec_sd),alpha=0.1,fill="orange")+
  geom_line(aes(y=rePrec_Mean+rePrec_sd),color='orange')+
  geom_line(aes(y=rePrec_Mean-rePrec_sd),color='orange')+
  scale_x_continuous(breaks = seq(0,35,by = 5))+
  theme_linedraw()
#prec
gridExtra::grid.arrange(sens,bacc,spec,prec)
```

```{r}
library(ztable)
library(tibble)
experiments <- c("5f-1s", "10f-1s", "15f-1s", "20f-1s", "25f-1s")
experiments_no_log <-
  c("5f-1s-no-log",
    "10f-1s-no-log",
    "15f-1s-no-log",
    "20f-1s-no-log",
    "25f-1s-no-log",
    "5f-1s-no-log-1d-loocvtune")
experiments <- c(experiments_no_log)

options(ztable.type = 'viewer')
r2 <- readr::read_csv("../../../resample.csv")
r2 <- r2 %>% filter(Experiment %in% experiments)
activity_metrics <-
  r2 %>% filter(Experiment == "15f-1s-no-log") %>% select(
    Experiment,
    reSens_R_Mean,
    reSens_GM_Mean,
    reSens_W_Mean,
    reSens_G_Mean,
    rePrec_R_Mean,
    rePrec_GM_Mean,
    rePrec_W_Mean,
    rePrec_G_Mean,
    reSpec_R_Mean,
    reSpec_GM_Mean,
    reSpec_W_Mean,
    reSpec_G_Mean
  ) %>%
  tidyr::pivot_longer(
    !Experiment,
    names_to = c("Activity", "Metric"),
    names_pattern = "re(.*)_(.*)_Mean",
    values_to = "count"
  ) %>%
  tidyr::pivot_wider(names_from = Metric, values_from = c(count)) %>% as.data.frame() %>% select(!Experiment)

all_metrics <-
  r2 %>% filter(Experiment == "15f-1s-no-log") %>% select(
    Experiment,
    reAcc_Mean,
    reKappa_Mean,
    reSens_Mean,
    reSens_Mean,
    rePrec_Mean,
    reSpec_Mean
  ) %>% t() %>% as.data.frame()

all_metrics <- all_metrics %>% slice(2:6)
all_metrics$V1 <- as.double(all_metrics$V1)
all_metrics <- all_metrics %>%
  add_column(all_metrics) %>%
  add_column(all_metrics) %>%
  add_column(all_metrics) %>% rownames_to_column("Metrics")

all_metrics$Metrics <- c("Accuracy",
                         "Kappa",
                         "Sensitivity",
                         "Specificity",
                         "Precision")

activity_metrics <- activity_metrics %>% rename(Metrics = "Activity")
activity_metrics$Metrics <- c("Sensitivity", "Precision", "Specificity")

names(all_metrics) <- names(activity_metrics)
rgroup = c("Overall", "Per Activity")
n.rgroup = c(5, 3)

table_15f_1s_no_log <- 
rbind(all_metrics, activity_metrics) %>%
  ztable(align = "llll", longtable = TRUE) %>% spanCol(row = 2, from = 3, to =
                                                         6) %>%
  spanCol(row = 3, from = 3, to = 6) %>%
  spanCol(row = 4, from = 3, to = 6) %>%
  spanCol(row = 5, from = 3, to = 6) %>%
  spanCol(row = 5, from = 3, to = 6) %>%
  spanCol(row = 6, from = 3, to = 6) %>%
  addrgroup(rgroup = rgroup,
            n.rgroup = n.rgroup,
            cspan.rgroup = 1) %>% hlines(add = c(5))

table_25f_1s_no_log
table_15f_1s_no_log
```



# Calculate LOOCV results

use `dvc exp show --drop ".*" --keep "loo.*mean_*|Experiment" --csv >loocv_results.csv`
```{r}
library(ztable)
options(ztable.type='viewer')

experiments_no_log <-
  c("5f-1s-no-log-1d-loocvtune",
    "10f-1s-no-log-1d-loocvtune",
    "15f-1s-no-log-1d-loocvtune",
    "20f-1s-no-log-1d-loocvtune",
    "25f-1s-no-log-1d-loocvtune",
    "30f-1s-no-log-1d-loocvtune",
    "35f-1s-no-log-1d-loocvtune"
    )
experiments <- c(experiments_no_log)
r<-readr::read_csv("../../../loocv_results.csv")
r <- r %>% filter(Experiment %in% experiments)
names(r)<-names(r)  %>% gsub(pattern = "loo(.*)_(.*)_mean", replacement = "\\2_\\1", x = names(r))

#options(ztable.type = 'latex')
options(ztable.zebra=NULL)
create_loocv_restable("5f-1s-no-log-1d-loocvtune",r)  
```

# Calculate Test results experiments (per animal)

use `dvc exp show  --drop ".*" --keep "Testloo.*mean_*|Experiment" --csv >Testloo_results.csv`

```{r}
library(ztable)
options(ztable.type='viewer')
r<-readr::read_csv("../../../Testloo_results.csv")
names(r)<-names(r)  %>% gsub(pattern = "Testloo(.*)_(.*)_mean", replacement = "\\2_\\1", x = names(r))
names(r)<-names(r)  %>% gsub(pattern = "Test(.*)", replacement = "\\1", x = names(r))

names(r)
options(ztable.zebra=NULL)
options(ztable.type = 'viewer')
create_loocv_restable("5f-1s-no-log-1d-loocvtune",r)  
```


# Calculate test results experiments (considering the complete testdataset as a whole)

use `dvc exp show  --drop ".*" --keep "test.*|Experiment" --csv >test_results.csv`
```{r}
library(ztable)
options(ztable.type='viewer')
r<-readr::read_csv("../../../test_results.csv")
names(r)<-names(r)  %>% gsub(pattern = "test(.*)_(.*)", replacement = "\\2_\\1", x = names(r))
names(r)<-names(r)  %>% gsub(pattern = "test(.*)", replacement = "\\1", x = names(r))

names(r)<-names(r)  %>% gsub(pattern = "macro_(.*)", replacement = "loo\\1_mean_macro", x = names(r))
names(r)
# looSens_mean_macro
options(ztable.zebra=NULL)
options(ztable.type = 'viewer')
create_loocv_restable("5f-1s-no-log-1d-loocvtune",r)  
```
```{r}
dataset <- readr::read_delim("data/split/seba-caprino_loocv.tsv",delim='\t')
goat_model <- readRDS("models/boost/seba-caprino_model.rds")

predictions<-predict(goat_model,dataset)
cm<-caret::confusionMatrix(reference=as.factor(dataset$Activity),predictions)
p_act_res<-cm$byClass %>% as.data.frame() %>% select(Sensitivity,Precision,Specificity) %>% t() %>% as.data.frame() 
names(p_act_res) <- gsub(pattern = "Class: (.*)", replacement = "\\1", x = names(p_act_res))
p_act_res %>% mutate_all(.funs=funs(round(.,2))) %>%  select(R,GM,W,G)
```



